Preprocessing

### 2024-08-12 nbs/guides/preprocessing/preprocessing.qmd
chore(nbs): freeze preprocessing
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Preprocessing
execute: 
  freeze: false
  eval: true
  warning: false
  error: false
  cache: true
toc: true
number-sections: true
highlight-style: gruvbox
csl: ../../bibstyle.csl
lightbox: auto
format:
  html:
    html-math-method: katex
  ipynb: default
---

>>>>

---
title: Preprocessing
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
toc: true
number-sections: true
highlight-style: gruvbox
csl: ../../bibstyle.csl
lightbox: auto
format:
  html:
    html-math-method: katex
  ipynb: default
---
